Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-15 paper.tex
Rephrase the reason for JavaScript isomorphism.  (More Alan Kay feedback.)

We have developed a block-oriented view of JavaScript, which we call
TurtleScript~\cite{turtlescript}.
The TurtleScript dialect of JavaScript is the single
implementation language for Nell.%
\footnote{Since JSON is the data-oriented subset of JavaScript,
our examples in Figures~\ref{fig:rules} and \ref{fig:aiml} are valid
TurtleScript.} % XXX: use TurtleScript tiles for the figures?
TurtleScript scales from Logo-like
pedagogical tasks (in subsets of the language) up to the
implementation of TurtleScript and the
Nell system itself.  As Figure~\ref{fig:turtlescript} shows,
TurtleScript's block view is isomorphic to
JavaScript's standard textual
representation to preserve the code-reading skills of existing
programmers.  We have begun implementation of a
tablet programming environment for TurtleScript which uses
drag-and-drop, direct interaction, and intelligent prompting to reduce
text entry requirements.

>>>>

We have developed a block-oriented view of JavaScript, which we call
TurtleScript~\cite{turtlescript}.
The TurtleScript dialect of JavaScript is the single
implementation language for Nell.%
\footnote{Since JSON is the data-oriented subset of JavaScript,
our examples in Figures~\ref{fig:rules} and \ref{fig:aiml} are valid
TurtleScript.} % XXX: use TurtleScript tiles for the figures?
TurtleScript scales from Logo-like
pedagogical tasks (in subsets of the language) up to the
implementation of TurtleScript and the
Nell system itself.  As Figure~\ref{fig:turtlescript} shows,
TurtleScript's block view is isomorphic to
JavaScript's standard textual
representation to
% CSA: hard to state all the reasons in just one short phrase, sigh.
ensure the readability of and compatibility with existing JavaScript libraries.
%preserve the code-reading skills of existing programmers.
%
We have begun implementation of a
tablet programming environment for TurtleScript which uses
drag-and-drop, direct interaction, and intelligent prompting to reduce
text entry requirements.
